---
title       : mpg prediction 
subtitle    : 
author      : Jim Smith
job         : student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## mpg prediction application using Shiny

### decided on using motor trends car data
Do some exploratory analysis

```{r}
data(mtcars)
head(mtcars)
```

--- .class #id

## linear regresssion 

### predicted mpg based on weight (wt) and cylinders (cyl)

```{r, echo=FALSE, eval=TRUE}
library(shiny)
data(mtcars)
```
```{r echo=FALSE, eval=FALSE}  
attach(mtcars)
```
```{r, echo=FALSE}
par(mfrow=c(1,2))
plot(wt, mpg, main="Car mpg vs weight ", 
                     xlab="Car Weight, 1000s of pounds ", ylab="Miles Per Gallon ", pch=19)
fit = lm(mpg~wt)  # for weight
abline(fit , col="red") # regression line (y~x)

plot(cyl, mpg, main="Car mpg vs cylinders", 
     xlab="cylinders ", ylab="Miles Per Gallon ", pch=19)
fit = lm(mpg~cyl)
abline(fit , col="red") # regression line (y~x) 
```

--- .class #id

## create ui.R and server.R
The ui is created within the shinyUI function. I used the pageWithSidebar.
```{r eval=FALSE}
shinyUI(pageWithSidebar(
    headerPanel("Shiny project, predict mpg"),
    sidebarPanel(),
    mainPanel(   )
    ))

```
The server code is a function with input and output inside a shinyServer function
```{r eval=FALSE}
shinyServer(
    function(input, output){
    }
)
```

--- .class #id

## final output
### after ui.r and server.r are complete, shinyapps.deployApp('file')

```{r fig.width=10, fig.height=5, echo=FALSE}
library(png)
library(grid)
img <- readPNG('assets/img/ShinyOutput.PNG')
 grid.raster(img)

